Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-09-30 main.tex
Completed Algorithm section - explanation of steps and references to the algorithms - summary picture after algorithms Update tikz picture to be correct (forgot encoding and some other notation)

    % Bounding rectangles
    \draw [gray] (0,23.25) rectangle (10,14.25);
    \draw [gray] (0,14) rectangle (10,5.5);
\end{tikzpicture}
\vspace{\baselineskip}
\caption{Required linear-combination aggregation steps at time $t$}
\label{fig:agg_steps}
\end{figure}

@@

\subsection{Integer Encoding for Real Numbers}
In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x : x \in \mathbb{Z}_N\}$. For this reason, a quantisation and integer mapping method for real numbers is required for their encryption and homomorphic processing. We quantise with a generalised Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.

@@

This encoding scheme provides the following homomorphic operations,
\begin{equation}
    \begin{split}
        \mathsf{E}_{N,f,m}(a_1) + \mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
        &\mathsf{E}_{N,f,m}(a_1+a_2)
    \end{split}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mathsf{E}_{N,f,m}(a_1)\mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
        &\mathsf{E}_{N,f,m+1}(a_1a_2)\,,
    \end{split}
\end{equation}
noting that the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:our_scheme_lin_comb}.

@@

\subsection{Algorithm}
% Maybe name the scheme? That would be in the heading here
Piece together the whole algorithm here.
Give the algorithm as pseudocode (including encoding and encryption, possible as separate procedures)

% assume f known to all, and public/private keys already distributed
% Note the abbreviation for encoding E (no N and f)
% Note the different m using in Encoding when computing alphas and betas

\begin{algorithm}
    \caption{Navigator Prediction Step}\label{alg:nav_prediction}
    \begin{algorithmic}[1]
        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$}

@@

\begin{algorithm}
    \caption{Measurement at Sensor $i$}\label{alg:measurement_info}
    \begin{algorithmic}[1]
        \Procedure{Measurement}{$i$, $s_{x,i}$, $s_{y,i}$, $r_i$, $N$, $H$}

@@

\begin{algorithm}
    \caption{Navigator Update Step}\label{alg:nav_update}
    \begin{algorithmic}[1]
        \Procedure{Update}{$\rvec{x}_{k}$, $\mat{P}_{k}$, $N$, $\lambda$}

@@

@@

    \fill [lightgray]  (0.25,4.75) rectangle (7.75,3.75);
    \node at (4,4.25) {$\langle\mathcal{E}_{pk_0}(\rv{\omega}): \rv{\omega} \in \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{x}_k\rv{y}_k, \rv{x}_k, \rv{y}_k\}\rangle$};

@@

    \fill [lightgray]  (0.25,-1.25) rectangle (3.75,-2.25);
    \node at (2,-1.75) {$\mathcal{E}_{pk_0}(\rvec{i}'_{k,1})$, $\mathcal{E}_{pk_0}(\mat{I}'_{k,1})$};
    \fill [lightgray]  (4.25,-1.25) rectangle (7.75,-2.25);
    \node at (6,-1.75) {$\mathcal{E}_{pk_0}(\rvec{i}'_{k,n})$, $\mathcal{E}_{pk_0}(\mat{I}'_{k,n})$};

@@

\end{tikzpicture}
\vspace{\baselineskip}
\caption{Alg summary}
\label{fig:agg_steps}
\end{figure}

>>>>

    % Bounding rectangles
    \draw [gray] (0,23.25) rectangle (10,14.25);
    \draw [gray] (0,14) rectangle (10,5.5);
\end{tikzpicture}
\vspace{\baselineskip}
\caption{Required linear-combination aggregation steps at time $t$.}
\label{fig:agg_steps}
\end{figure}

@@

\subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}
In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x : x \in \mathbb{Z}_N\}$. For this reason, a quantisation and integer mapping method for real numbers is required for their encryption and homomorphic processing. We quantise with a generalised Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.

@@

This encoding scheme provides the following homomorphic operations,
\begin{equation}
    \begin{split}
        \mathsf{E}_{N,f,m}(a_1) + \mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
        &\mathsf{E}_{N,f,m}(a_1+a_2)
    \end{split}\label{eqn:encoding_homomorphic_add}
\end{equation}
and
\begin{equation}
    \begin{split}
        \mathsf{E}_{N,f,m}(a_1)\mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
        &\mathsf{E}_{N,f,m+1}(a_1a_2)\,,
    \end{split}
\end{equation}
noting that the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:our_scheme_lin_comb}.

@@

\subsection{Algorithm} \label{subsec:algorithm}
In this section, we piece together our LCAO secure encryption scheme in Section \ref{sec:our_scheme} with the modified measurement model in Sections \ref{subsec:observation_model} and \ref{subsec:range_measurement_mod} and define our privacy-preserving localisation algorithm.

The privacy-preserving localisation filter can be described by the following steps.
\begin{description}
    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{sec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly. Additionally, we assume that fractional precision $f$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors. We will thus simplify the encoding notation $\mathsf{E}_{N,f,m}(\cdot)$ to $\mathsf{E}_{m}(\cdot)$.

    \item[Prediction] The navigator computes the typical EKF prediction equations before encrypting state variables and broadcasting to sensors. This is given by Algorithm \ref{alg:nav_prediction}.

    \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,1}$ and $\mat{I}'_{k,1}$, encrypting them for aggregation, and sending them back to the navigator. Care must be taken when encoding during homomorphic operations to ensure fractional factor $m$ satisfies \eqref{eqn:encoding_homomorphic_add}. This has been described by Algorithm \ref{alg:measurement_info}.

    \item[Update] The navigator aggregates measurement vectors and matrices before decrypting them. The typical EIF update equations can then be computed. This is shown in Algorithm \ref{alg:nav_update}.
\end{description}

\begin{algorithm}[htbp]
    \caption{Navigator Prediction}\label{alg:nav_prediction}
    \begin{algorithmic}[1]
        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$}

@@

\begin{algorithm}[htbp]
\caption{Measurement at Sensor $i$}\label{alg:measurement_info}
\begin{algorithmic}[1]
    \Procedure{Measurement}{$i$, $s_{x,i}$, $s_{y,i}$, $r_i$, $N$, $H$}

@@

\begin{algorithm}[htbp]
\caption{Navigator Update}\label{alg:nav_update}
\begin{algorithmic}[1]
    \Procedure{Update}{$\rvec{x}_{k}$, $\mat{P}_{k}$, $N$, $\lambda$}

@@

Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have been summarised graphically in Figure \ref{fig:alg_steps}, where encryptions and encodings of vectors and matrices have been denoted with $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_m(\cdot)$ for brevity, and represent element-wise operations with the same parameters.

@@

    \fill [lightgray]  (0.25,5) rectangle (7.75,4);
    \node at (4,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})): \rv{\omega} \in \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{x}_k, \rv{y}_k\}\rangle$};

@@

    \fill [lightgray]  (0.5,-1.25) rectangle (3.5,-2.25);
    \node[align=center] at (2,-1.75) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\rvec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
    \fill [lightgray]  (4.5,-1.25) rectangle (7.5,-2.25);
    \node[align=center] at (6,-1.75) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\rvec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};

@@

\end{tikzpicture}
\vspace{\baselineskip}
\caption{The summary of steps involved in our proposed privacy-preserving EIF.}
\label{fig:alg_steps}
\end{figure}
